Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-04-22 03-SCPME.Rmd
minor adjustments

\newpage
```{r, eval = T, echo = F, fig.cap = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)"}

# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(error = mean(Error), sd = sd(Error)) %>% arrange(error) %>% pander(caption = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")

>>>>

\newpage
```{r, eval = T, echo = F, fig.cap = "Average model error for dimension p = 150."}

# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% rename(Model = model, error = Error) %>% group_by(Model) %>% summarise(Error = mean(error), SD = sd(error)) %>% arrange(Error) %>% pander(caption = "Average model error for dimension p = 150.")

### 2019-04-22 index.Rmd
minor adjustments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE, out.width = "85%", fig.align = "center", out.extra = "")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE, tidy.opts = list(width.cutoff = 60), out.width = "85%", fig.align = "center", out.extra = "")

@@

# Preface {-}

I would like to thank my advisor Professor Adam Rothman for his guidance and support this past year. His enthusiasm towards this research area is ultimately what got me interested and I truly enjoyed having the opportunity to learn from him.

My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school's challenges extend far beyond the classroom and I'm so lucky to have you by my side.
